### 2020-03-14 Strings2020/strings2/strings2.tex
Add strings2 & update CI

\newcommand{\hwNumber}{1}

@@

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}

@@

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}
	\begin{enumerate}
	\item \textbf{Read \textit{Polchinski} Sections 1.3 and 1.4}:

	Read, \textit{mostly} understood. \qed

>>>>

\newcommand{\hwNumber}{2 [WIP]}

@@

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\usepackage{cancel}

@@

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}
	\begin{enumerate}
	\item \textbf{BRST Quantization of Bosonic String}: 
	\begin{gather}
		S = S^X + S^{bc},\\
		S^X = - \frac{1}{2\pi\alpha'} \int\dd[2]{z}
			\pd X^\mu \pdbar X_\mu,\quad
		S^{bc} = \frac{1}{2\pi} \int\dd[2]{z}
			\pqty\Big{
				b\,\pdbar c
				+ \tilde{b}\,\pd\tilde{c}
			}
	\end{gather}
	This is the gauge fixed action. The corresponding BRST transformation is listed in \textit{Polchinski}; for each of the subsystems, we have its (classical) energy-momentum:
	\begin{equation}
		T^X(z)
		= - \frac{1}{\alpha'}\,
			\normorder{\pd X^\mu \pd X_\mu}\,,\quad
		\tilde{T}^X(\bar{z})
		= - \frac{1}{\alpha'}\,
			\normorder{\pdbar X^\mu \pdbar X_\mu}\,,
		\\[.5ex]
		T^{bc}(z) = \normorder{(\pd b)\,c}
			- 2\,\pd(\normorder{bc}),\quad
		\tilde{T}^{bc}(\bar{z}) = \normorder{
			(\pdbar \tilde{b})\,\tilde{c}
		} - 2\,\pdbar(\normorder{
			\tilde{b}\tilde{c}
		}),
	\end{equation}

	\begin{enumerate}
	\item To get the energy-momentum of $S$, let's visit each of the subsystems respectively; first, BRST transformation of $X$ is given by:
	\begin{equation}
		\var{X^\mu}
		= i\epsilon\,\pqty{
			c\pd + \tilde{c}\pdbar
		} X^\mu
	\end{equation}
	Compared with the conformal transformation\footnote{
		We follow the convention of \textit{Polchinski} unless otherwise stated. 
	}: $
		\var{X^\mu}
		= -\epsilon\,\pqty{
			v\pd
			+ \tilde{v}\pdbar
		} X^\mu
	$, we see that they are in fact identical under the equivalence $
		-\epsilon v \sim i\epsilon c,\ %
		-\epsilon \tilde{v} \sim i\epsilon \tilde{c}
	$, hence we can simply follow the derivation of conformal current and write down $\var{S}^X$'s contribution to the conserved current:
	\begin{equation}
		j^X = c(z)\,T^X(z)
	\end{equation}

	The transformation of $b,c$ is less obvious; for holomorphic current, we need only focus on the holomorphic part of $S^{bc}$; on-shell variation yields:
	\begin{equation}
		0 = \var{S}^{bc}
		= \pqty{\frac{1}{2\pi} \int \dd[2]{z} \pqty{
			- \pdbar c\,\var{b}
			- \pdbar b\,\var{c}
		}}_{\!\!=\mspace{1mu}0}
		+ \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar\epsilon\,\pqty\big{
				-ibc\,\pd c
			} 
	\end{equation}
	Here we've plugged in $
		\var{c} = i\epsilon(z,\bar{z})\,c\pd c
	$, and we have moved $\pdbar\epsilon$ to the beginning of the expression, while respecting the anti-commuting nature of $\epsilon$. With a conventional $i$ coefficent (which agrees with the convention of $j^X$), we have $bc$'s contribution to the conserved current:
	\begin{equation}
		j^{bc} = i\,\pqty\big{
			-ibc\,\pd c
		} = bc\,\pd c
	\end{equation}

	Note that $j^{bc}$ is, in fact, related to the energy-momentum (at least classically):
	\begin{equation}
		\frac{1}{2}\,cT^{bc}
		= \frac{1}{2}\,c\,{(\pd b)\,c}
			- c\,\pd({bc})
		= - c\,\pd({bc})
		= - cb\,\pd c
		= bc\,\pd c = j^{bc}
	\end{equation}
	Hence we have the classical BRST current:
	\begin{equation}
		j(z) = c(z)\,\pqty{
			T^X + \frac{1}{2}\,T^{bc}
		}
	\end{equation}

	For a quantum version, redefine $j(z)$ with normal ordering, and we have:
	\begin{gather}
		T(z)\,j(0)
		\sim T^X(z)\,T^X(0)\,c(0)
			+ T^{bc}(z)\,cT^X(0)
			+ T^{bc}(z)\,
				\normorder{bc\,\pd c}_{\,(0)},
		\label{eq:BRST_Tj_OPE}\\
		\text{where}\quad
		T^X(z)\,T^X(0)\,c(0)
		\sim \pqty{
			\frac{D}{2z^4}
			+ \frac{2}{z^2}\,{T^X(0)}
			+ \frac{1}{z}\,{\pd T^X(0)}
		}\,c(0),
		\label{eq:BRST_Tj_OPE_partI}
	\end{gather}
	Here we've used the fact that $X$ and $b,c$ is de-coupled in the gauge-fixed action, hence their OPE is trivial. Also, we've expanded the first term using $TT$ OPE of the free boson. Additionally, note that $c(z)$ is primary with weight $(-1,0)$, we have:
	\begin{equation}
	\begin{aligned}
		T^{bc}(z)\,cT^X(0)
		&\sim \Bqty{T^{bc}(z)\,c(0)}\,T^X(0) \\
		&\sim \pqty{
			\frac{-1}{z^2}\,c(0)
			+ \frac{1}{z}\,\pd c(0)
		}\,T^X(0),
	\end{aligned}
	\label{eq:BRST_Tj_OPE_partII}
	\end{equation}
	The last term in \eqref{eq:BRST_Tj_OPE} can be brute-forced as follows:
	\begin{equation}
		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
		= \pqty\big{
			\normorder{(\pd b)\,c}
			- 2\,\pd(\normorder{bc})
		}_{(z)}\,\normorder{bc\,\pd c}_{\,(0)}\,,
	\end{equation}
	\vspace{-1\baselineskip}
	\begin{align}
		\normorder{(\pd b)\,c}_{\,(z)}\,
		\normorder{bc\,\pd c}_{\,(0)}
		&\sim \normorder{
			\wick{
				(\pd \c b)\,c_{(z)}\,
				b\c c\,\pd c_{(0)}
			}
		} + \normorder{
			\wick{
				(\pd \c b)\,c_{(z)}\,
				bc\,\pd \c c_{(0)}
			}
		} + \normorder{
			\wick{
				(\pd b)\,\c c_{(z)}\,
				\c b c\,\pd c_{(0)}
			}
		} \notag\\
		&\qquad + \normorder{
			\wick{
				(\pd \c1 b)\,\c2 c_{(z)}\,
				\c2 b \c1 c\,\pd c_{(0)}
			}
		} + \normorder{
			\wick{
				(\pd \c1 b)\,\c2 c_{(z)}\,
				\c2 bc \,\pd \c1 c_{(0)}
			}
		} \notag\\[.5ex]
		&\sim \frac{-1}{z^2}\,(+1)\,\normorder{
			c_{(z)}\,b\,\pd c_{(0)}
		} + \frac{-2}{z^3}\,(-1)\,\normorder{
			c_{(z)}\,bc_{(0)}
		} + \frac{1}{z}\,(+1)\,\normorder{
			\pd b_{(z)}\,c\pd c_{(0)}
		} \notag\\
		&\qquad + \frac{-1}{z^2}\cdot\frac{1}{z}\,
			(+1)\,\pd c(0)
		+ \frac{-2}{z^3}\cdot\frac{1}{z}\,
			(-1)\,c(0) \notag\\[.5ex]
		&\sim \frac{-1}{z^2}\,\pqty{
			-j^{bc}(0) + \order*{z^2}
		} + \frac{2}{z^3}\,\pqty{
			z\,j^{bc}(0)
			+ \frac{z^2}{2}\,\normorder{
				bc\,\pd^2 c
			}_{\,(0)}
			+ \order*{z^3}
		} \notag\\[-.3ex]
		&\qquad + \frac{1}{z}\,\pqty\big{
			\normorder{
				(\pd b)\,c\,\pd c
			}_{\,(0)} + \order{z}
		} + \frac{-1}{z^3}\,\pd c(0)
			+ \frac{2}{z^4}\,c(0) \notag\\[.7ex]
		&\sim \frac{4}{2z^4}\,c(0)
			+ \frac{-1}{z^3}\,\pd c(0)
			+ \frac{3}{z^2}\,j^{bc}(0)
			+ \frac{1}{z}\,\normorder{\pqty{
				bc\,\pd^2 c
				+ (\pd b)\,c\,\pd c
			}}_{\,(0)}\,, \notag\\[1ex]
		&\sim \frac{4}{2z^4}\,c(0)
			+ \frac{-1}{z^3}\,\pd c(0)
			+ \frac{3}{z^2}\,j^{bc}(0)
			+ \frac{1}{z}\,\pd j^{bc}(0), \\[3ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		THIS IS INSANE!
%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\normorder{bc}_{\,(z)}\,
		\normorder{bc\,\pd c}_{\,(0)}
		&\sim \normorder{
			\wick{
				\c1 b c_{(z)}\,
				b \c1 c\, \pd c_{(0)}
			}
		} + \normorder{
			\wick{
				\c1 b c_{(z)}\,
				b c\, \pd \c1 c_{(0)}
			}
		} + \normorder{
			\wick{
				b \c1 c_{(z)}\,
				\c1 b c\, \pd c_{(0)}
			}
		} \notag\\
		&\qquad + \normorder{
			\wick{
				\c1 b \c2 c_{(z)}\,
				\c2 b \c1 c\, \pd c_{(0)}
			}
		} + \normorder{
			\wick{
				\c1 b \c2 c_{(z)}\,
				\c2 b c\, \pd \c1 c_{(0)}
			}
		} \notag\\[.5ex]
		&\sim \frac{1}{z}\,(+1)\,\normorder{
			c_{(z)}\,b\,\pd c_{(0)}
		} + \frac{1}{z^2}\,(-1)\,\normorder{
			c_{(z)}\,bc_{(0)}
		} + \frac{1}{z}\,(+1)\,\normorder{
			b_{(z)}\,c\pd c_{(0)}
		} \notag\\
		&\qquad + \frac{1}{z}\cdot\frac{1}{z}\,
			(+1)\,\pd c(0)
		+ \frac{1}{z^2}\cdot\frac{1}{z}\,
			(-1)\,c(0) \notag\\[1ex]
		&\sim \frac{1}{z}\,\pqty\big{
			-j^{bc}(0)
		} + \frac{-1}{z^2}\,\pqty\big{
			z\,j^{bc}(0)
		} + \frac{1}{z}\,\pqty\big{
			j^{bc}(0)
		} + \frac{1}{z^2}\,\pd c(0)
		+ \frac{-1}{z^3}\,c(0) \notag\\[1ex]
		&\sim \frac{-1}{z^3}\,c(0)
			+ \frac{1}{z^2}\,\pd c(0)
			+ \frac{-1}{z}\,j^{bc}(0), \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		DERIVATIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\pd (\normorder{bc})_{(z)}\,
		\normorder{bc\,\pd c}_{\,(0)}
		&\sim \frac{6}{2z^4}\,c(0)
			+ \frac{-2}{z^3}\,\pd c(0)
			+ \frac{1}{z^2}\,j^{bc}(0),
	\end{align}
	\begin{gather}
		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
		\sim \frac{-8}{2z^4}\,c(0)
			+ \frac{3}{z^3}\,\pd c(0)
			+ \frac{1}{z^2}\,j^{bc}(0)
			+ \frac{1}{z}\,\pd j^{bc}(0),
		\label{eq:BRST_Tj_OPE_partIII}\\[2ex]
		T(z)\,j(0)
		\sim \eqref{eq:BRST_Tj_OPE_partI}
			+ \eqref{eq:BRST_Tj_OPE_partII}
			+ \eqref{eq:BRST_Tj_OPE_partIII}
		\sim \frac{D-8}{2z^4}\,c(0)
			+ \frac{3}{z^3}\,\pd c(0)
			+ \frac{1}{z^2}\,j(0)
			+ \frac{1}{z}\,\pd j(0),
	\end{gather}

	We see that $j(z)$ defined with na\"ive normal ordering is \textit{almost} but \textit{not quite} a primary. It differs from primary OPE at $\order{\frac{1}{z^4}}$ and $\order{\frac{1}{z^3}}$. However, it is possible to make it into a primary by adding extra terms that do not interfere with current conservation $\pdbar j = 0$. To cancel the $\frac{3}{z^3}\,\pd c(0)$ term, notice that $
		b(z)\,\pd^2 c(0) \sim \frac{2}{z^3}
	$, therefore it may be helpful to look at:
	\begin{equation}
	\begin{aligned}
		T(z)\,\pd^2 c(0)
		\sim T^{bc}(z)\,\pd^2 c(0)
		&\sim \pd^2_w \pqty{
			T^{bc}(z)\,c(w)
		}_{w\to 0} \\
		&\sim \pd^2_w \pqty{
			\frac{-1}{(z-w)^2}\,c(w)
			+ \frac{1}{z-w}\,\pd c(w)
		}_{\!w\to 0} \\[.5ex]
		&\sim \frac{-12}{2z^4}\,c(0)
			+ \frac{-2}{z^3}\,\pd c(0)
			+ \frac{1}{z^2}\,\pd^2 c(0)
			+ \frac{1}{z}\,\pd^3 c(0),
	\end{aligned}
	\end{equation}
	Again we've used $Tc$ OPE of the primary $c(w)$. We see that indeed, the $\frac{1}{z^3}\,\pd c(0)$ term can be canceled by shifting $j(z)$:
	\begin{gather}
		j(z)\ \longmapsto\ j(z)
			+ \frac{3}{2}\,\pd^2 c(z),\quad
		j(z) = j^X + j^{bc}
			+ \frac{3}{2}\,\pd^2 c,\\[1ex]
		T(z)\,j(0)
		\sim \frac{D-26}{2z^4}\,c(0)
			+ \frac{1}{z^2}\,j(0)
			+ \frac{1}{z}\,\pd j(0),
	\end{gather}

	We see that $j(z)$ defined in this way is a primary of weight $(1,0)$ in $D = 26$. This is the quantum BRST current. 
	\qedfull

%	note that $b,c$ are primaries with weight $(2,0)$ and $(-1,0)$, hence $Tb,Tc$ OPEs take the standard form of a $T\cdot(\text{primary})$ OPE. We have:
%	\begin{equation}
%	\begin{aligned}
%		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
%		&\sim \pqty{
%				\frac{2}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					(\pd b)\,c\pd c
%				}
%			} \\
%		&\phantom{\sim \quad}
%			+ \pqty{
%				\frac{-1}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					b\,(\pd c)(\pd c)
%				}
%			} \\
%		&\phantom{\sim \quad}
%			+ \pqty{
%				\frac{-1}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					bc\,\pd^2 c
%				}
%			} \\
%		&\sim \frac{1}{z}\,\pd\,
%			\normorder{bc\,\pd c}
%		\sim \frac{1}{z}\,\pd\,\pqty{
%			j - cT^X
%		}_{(0)} \\
%		&\sim \frac{1}{z}\,\pd j(0)
%		- \frac{1}{z}\,c(0)\,\pd T^X(0)
%		- \frac{1}{z}\,T^X(0)\,\pd c(0),
%	\end{aligned}\\
%		T(z)\,j(0)
%		\sim \frac{D}{2z^4}\,c(0)
%			+ \frac{2}{z^2}\,T^X(0)\,c(0)
%			+ \frac{1}{z}\,\pqty{
%				\pd j(0)
%				- T^X(0)\,\pd c(0)
%			}
%	\end{equation}

	\item

	\item \textbf{Linear Dilaton CFT:}

	\clearpage

	\quad
	\vfill\pagebreak
